Light inextensible strings under tension in the Schwarzschild geometry

### 2019-03-21 string_ajp.tex
typos

\begin{abstract}
Here I analyze the behaviour of stationary, light inextensible strings
under tension in the vicinity of a nonrotating black hole.  Such
strings minimize their proper length, given by integrating the spatial
component of the Schwarzshild metric along the string.  The path is
calculated by numerical solution to the Euler-Lagrange equations.  If
the string is entirely outside the event horizon, its closest approach
is to the singularity is tangential; if the distance of closest
approach is less than about $1.076109317$ Schwarzschild radii, the
string self-intersects.  If the string attains $r=2GM/c^2$, then it
will in general be tangential to the event horizon.  Light taut
strings interpret the concept ``straight line'' and their behaviour
suggests a possible way of manipulating a black hole.
\end{abstract}
% AJP requires an abstract for all regular article submissions.
% Abstracts are optional for submissions to the "Notes and Discussions" section.

@@

\subsection{Nonradial string}
Integrating along a path between two
points~$p_1=\left(r_1,\phi_1\right)$ and~$p_2=\left(r_2,\phi_2\right)$
gives the {\em proper} length of the path, which is the length of an
inextensible string joining~$p_1$ and~$p_2$.  A taut but light string
from~$p_1$ to~$p_2$ will adopt an extremal-length path.  Such paths
may be found by the calculus of variations; parametrizing a curve in
terms of~$r=r\left(\phi\right)$ gives us a path length of

@@

Light inextensible strings under tension adopt non-trivial
configurations including self-intersecting paths.  The path of such
strings furnishes an interpretation of the concept ``straight line''
in general relativity, others being null geodesics and world lines of
massive objects.  Comparing a world line with that of nearby taut
strings thus furnishes another insight into path curvature,
complementing the analysis of Abramowicz~\cite{abramowicz1992}.

>>>>

\begin{abstract}
Here I analyze the behaviour of stationary, light inextensible strings
under tension in the vicinity of a nonrotating black hole.  Such
strings minimize their proper length, given by integrating the spatial
component of the Schwarzschild metric along the string.  The path is
calculated by numerical solution to the Euler-Lagrange equations.  If
the string is entirely outside the event horizon, its closest approach
is to the singularity is tangential; if the distance of closest
approach is less than about $1.076109317$ Schwarzschild radii, the
string self-intersects.  If the string attains $r=2GM/c^2$, then it
will in general be tangential to the event horizon.  Light taut
strings interpret the concept ``straight line'' and their behaviour
suggests a possible way of manipulating a black hole.
\end{abstract}
% AJP requires an abstract for all regular article submissions.
% Abstracts are optional for submissions to the "Notes and Discussions" section.

@@

\section{Nonradial string}
Integrating along a path between two
points~$p_1=\left(r_1,\phi_1\right)$ and~$p_2=\left(r_2,\phi_2\right)$
gives the {\em proper} length of the path, which is the length of an
inextensible string joining~$p_1$ and~$p_2$.  A taut but light string
from~$p_1$ to~$p_2$ will adopt an extremal-length path.  Such paths
may be found by the calculus of variations; parametrizing a curve in
terms of~$r=r\left(\phi\right)$ gives us a path length of

@@

Light inextensible strings under tension adopt non-trivial
configurations including self-intersecting paths.  The path of such
strings interprets the concept ``straight line'' in general
relativity, others being null geodesics and world lines of massive
objects.  Comparing a world line with that of nearby taut strings thus
furnishes another insight into path curvature, complementing the
analysis of Abramowicz~\cite{abramowicz1992}.
